\documentclass[letterpaper, 10pt]{article}
\usepackage[margin=0.50in]{geometry}

\usepackage{calc}

\usepackage{sweet_resume}

\usepackage{enumitem}
\usepackage{tabularx}

\usepackage[T1]{fontenc}
\usepackage{setspace}

\usepackage[usenames,dvipsnames]{xcolor}

\pagenumbering{gobble}

\definecolor{BrOrange}{HTML}{FF7F00}

\definecolor{MariPro}{HTML}{D43247}
\definecolor{DarkDark}{HTML}{000044}
\definecolor{NGreenB}{HTML}{666633}

\definecolor{BrBlue}{HTML}{FF7F00}

\newcommand{\NrcColorName}{Black}
\newcommand{\NrcColorTitle}{RoyalBlue}
\newcommand{\NrcColorHeaderA}{MidnightBlue}
\newcommand{\NrcColorSubHeaderA}{MidnightBlue}
\newcommand{\NrcColorSubHeaderB}{Black}

\pdfinfo{
/Author (Nicholas Clark)
/Title  (Resume - Nicholas Clark)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\WorkExperienceLineOne}[2]{%
    \nrccolstring{\textcolor{\NrcColorSubHeaderA}{\textbf{#1}}}%
    {\textcolor{\NrcColorSubHeaderB}{\textbf{#2}}}%
}

\newcommand{\WorkExperienceLineTwo}[2]{%
    \nrccolstring{\small\textit{#1}}{\small\textit{#2}}%
}

\newcommand{\WorkExperienceMidBreak}{%
    \par \smallskip \smallskip%
}

\newcommand{\WorkExperienceEndBreak}{%
    \par\bigskip%
}

\newcommand{\makeheader}[1]{%
\begingroup%
    \noindent%
    \textcolor{\NrcColorHeaderA}{\Large \textbf{\textsc{#1\\}}}%
    \hfill%
\endgroup%
\hfill%
}
%

%%%%%%%%%%%%%%%%%%%%%%%%% Work Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\workRivian}{%
    \WorkExperienceLineOne {Rivian Automotive} {Palo Alto, CA}
    \WorkExperienceLineTwo {Senior Staff Software Engineer} {2022-present}
    \WorkExperienceLineTwo {Staff Software Engineer} {2022}
    \WorkExperienceMidBreak
    Architect and OS lead on upcoming residential energy products. Tech-lead
    for a team of 3 other developers.
    \WorkExperienceMidBreak

    Develop Yocto-based Linux distribution for use on a family of upcoming
    energy-storage systems.
    \WorkExperienceMidBreak

    Design and implement entire build flow, including CI/CD to internal teams.
    Migrate repos to Gitlab and use Gitlab CI/CD to run cloud-hosted AWS builds.
    \WorkExperienceMidBreak
}

\newcommand{\workCruise}{%
    \WorkExperienceLineOne {Cruise Automation} {San Francisco, CA}
    \WorkExperienceLineTwo {Senior Software Engineer II} {2021-2022}
    \WorkExperienceLineTwo {Senior Software Engineer} {2020-2021}
    \WorkExperienceMidBreak
    Software engineer for safety-critical systems. Design and
    maintain Buildroot-based Linux systems. Bootloader design and platform
    bringup. Mentor junior developers.
    \WorkExperienceMidBreak

    Implement build-reproducibility and A/B delta firmware update mechanism
    used on hardware in upcoming self-driving products. Work with Buildkite
    and Artifactory administrators to develop custom build plans.
    \WorkExperienceMidBreak
}

\newcommand{\workUA}{%
    \WorkExperienceLineOne {Universal Audio} {Boulder, CO}
    \WorkExperienceLineTwo {Senior System Software Engineer} {2019-2020}
    \WorkExperienceLineTwo {System Software Engineer} {2017-2019}
    \WorkExperienceMidBreak
    Software engineer and OS lead for realtime audio products. Develop and
    maintain Yocto-based Linux distributions.
    \WorkExperienceMidBreak

    Manage CI server, builds, deployment, and firmware updates for consumer
    products.
    \WorkExperienceMidBreak

    System software in C/C++, Python, and Bash. Train internal teams in
    cross-compilation methods.
    \WorkExperienceMidBreak
}

\newcommand{\workQSC}{%
    \WorkExperienceLineOne {QSC Systems} {Boulder, CO}
    \WorkExperienceLineTwo {Senior FPGA Firmware Engineer} {2015-2017}
    \WorkExperienceMidBreak
}

\newcommand{\workKarlStorz}{%
    \WorkExperienceLineOne {Karl Storz Imaging} {Goleta, CA}
    \WorkExperienceLineTwo {FPGA Firmware Engineer} {2013-2015}
    \WorkExperienceMidBreak

    FPGA lead on commercially-available medical camera systems. Worked closely
    with software, electrical and mechanical teams to develop successful
    products.
    \WorkExperienceMidBreak

    Wrote custom Verilog peripherals for communication and video, and wrote
    firmware for soft-core microcontrollers.
    \WorkExperienceEndBreak%
}


\newcommand{\workKarlStorzShort}{%
    \WorkExperienceLineOne {Karl Storz Imaging} {Goleta, CA}
    \WorkExperienceLineTwo {FPGA Firmware Engineer} {2013-2015}
    \WorkExperienceMidBreak
}

\newcommand{\workLthree}{%
    \WorkExperienceLineOne {L-3 Ocean Systems} {Goleta, CA}
    \WorkExperienceLineTwo {Electrical Engineer II} {2011-2013}
    \WorkExperienceLineTwo {Electrical Engineer I} {2007-2011}
    \WorkExperienceEndBreak%
}

\newcommand{\workMotionEng}{%
    \WorkExperienceLineOne {Motion Engineering, Inc} {Goleta, CA}
    \WorkExperienceLineTwo {Engineering Intern} {2006-2007}
    \WorkExperienceMidBreak
    Engineering intern. Worked with high-performance motion controllers used in
    semiconductor fab plants. Assisted in converting several product lines to
    be RoHS-compliant. Worked as a component engineer to solve obsolescence
    issues and suggest workarounds for unavailable parts. Interacted directly
    with global contractors. Auctioned and sold test equipment.
    \WorkExperienceEndBreak%
}

\newcommand{\workUCSBLifesci}{%
    \WorkExperienceLineOne {UCSB Life Sciences Department} {Goleta, CA}
    \WorkExperienceLineTwo {IT Helpdesk} {2004-2006}
    \WorkExperienceMidBreak
    Provided support for 800+ faculty, staff and graduate students in two
    academic departments and two interdisciplinary graduate programs.
    Responsible for basic and advanced troubleshooting to diagnose and
    resolve both hardware and software problems. Configured and maintained
    OS X, Linux, Windows, and FreeBSD computers.
    \WorkExperienceEndBreak%
}

\newcommand{\EducationUCSB}{%
    \WorkExperienceLineOne{University of California} {Santa Barbara, CA}
    \WorkExperienceLineTwo{B.S. Electrical Engineering}
    \WorkExperienceEndBreak%
}

\hyphenation{Micro-blaze}

\begin{document}%
%%%%%%%%%%%%%%% Title %%%%%%%%%%%%
\nrctitle
{\textcolor{\NrcColorName}{Nicholas Clark}}
{3161 San Angelo Way}
{Union City, CA 94587}
{805-636-4033}
{nicholas.clark@gmail.com}
%
\begin{center}\par\smallskip
\textcolor{\NrcColorTitle}{\Large \textbf{\textsc{Architect / Staff Software Engineer}}}\par
\large \textbf{{Software and Build Systems}}\par
\smallskip
\noindent \begin{minipage}[t]{0.75\textwidth}%
\begin{center}
Dynamic engineer with deep CI/CD experience as a developer and as a build
engineer. Specialties in embedded Linux firmware and build/test automation.
\end{center}
\end{minipage}
\end{center}
\par \smallskip \smallskip
%%%%%%%%%%%%% Column 1%%%%%%%%%%%%%%%
%
%    horizontal: leftmargin, rightmargin, itemindent, listparindent, labelwidth, labelsep
%    vertical: topsep, partopsep, parsep, itemsep
%
\newcommand{\MyColumnOne}{%
    \vspace{1.3mm}
    \setitemize[0]{leftmargin=*, parsep=0pt, itemsep=0pt, topsep=0pt, partopsep=0pt}%
    \noindent \begin{minipage}[t]{0.45\textwidth}%
    \par \smallskip \begin{spacing}{0.95}%

    \begin{flushleft} %
    \makeheader{CI/CD Systems} \par%
    \begin{itemize}%
        \item Collaboration with developers, test engineers, and release teams
        \item CI/CD pipelines and build-promotion workflows
        \item Git hosting and repo management
        \item Build automation with common CI platforms
        \item Scripting and build systems
        \item Packaging for Debian, Ubuntu, and Redhat systems
        \item Cross-compilation and specialized toolchains
        \item Scripting in Python, TCL, and Bash
        \item AWS administration
    \end{itemize}%
    \WorkExperienceMidBreak

    \makeheader{Software Tools} \par%
    %
    \WorkExperienceLineOne{Build Tools}{}
    \WorkExperienceMidBreak
    \begin{itemize}%
        \item Jenkins, Bamboo, and Gitlab CI systems
        \item Git repo hosting with Gitlab, Gitea, and  Gitolite/Gitweb
        \item CMake, Scons, and GNU Autotools build systems
        %\item Python Setuptools
        %\item Debian and Redhat package generation
    \end{itemize}%
    %
    \WorkExperienceMidBreak
    \WorkExperienceLineOne{Programming}{}
    \WorkExperienceMidBreak
    \begin{itemize}%
        \item Scripting with Bash, Python, and TCL \\
        \item C and C++ for Linux/POSIX and microcontrollers\\
        \item Cross-compilation toolchains\\
        \item Open-source software support\\
        \item Version control with Git\\
        \item Typesetting with \LaTeX\\

    \end{itemize}
    %
    \WorkExperienceMidBreak
    \WorkExperienceLineOne{General Computing}{}
    \WorkExperienceMidBreak
    \begin{itemize}%
        \item Linux, MacOS, FreeBSD, and Windows\\
        \item Hardware \& software troubleshooting\\
        \item Microsoft Office and Visio\\
        %\item Adobe Photoshop \& Illustrator\\
    \end{itemize}%
    \WorkExperienceMidBreak

    \makeheader{Software \& Firmware} \par%
    \begin{itemize}%
        \item Yocto and Buildroot-based systems
        \item Bootloaders and Linux kernel drivers
        \item System software in C, C++, Python, and Bash
        \item Cross-functional design
        \item Build automation and CI workflow
        \item Microcontroller and FPGA firmware
    \end{itemize}%/.
    \WorkExperienceMidBreak

    \makeheader{Hardware Engineering} \par%
    \begin{itemize}%
        \item Circuit-board bringup and troubleshooting
        \item Schematic capture/PCB design
        \item Mixed-signal circuit design techniques
        \item High-speed digital design
        \item Electronics manufacturing and DFM principles
    \end{itemize}%


\end{flushleft}%
\end{spacing} \end{minipage}%
}%
%%%%%%%%%%%%% Column 2%%%%%%%%%%%%%%%
\newcommand{\MyColumnTwo}{%
    \noindent \begin{minipage}[t]{0.45\textwidth}%
    \par \smallskip \begin{spacing}{0.95}%
    \vspace{2.45mm}

    \WorkExperienceMidBreak
    \makeheader{Work Experience} \par%
        \workRivian
        \workCruise
        \workUA
        \workQSC
        \workKarlStorzShort
        \workLthree
        %\workMotionEng
        %\workUCSBLifesci

    \makeheader{Education} \par%
        \EducationUCSB
    \end{spacing} \end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\nrctwocols
%\begin{center}$\bullet$\end{center}\par

\noindent\begin{tabularx}{\textwidth}{@{}X|X@{}}
\hline
{\MyColumnOne\hfill} & {\hfill\MyColumnTwo}
\end{tabularx}
\end{document}
