\documentclass[letterpaper, 10pt]{article}
\usepackage[margin=0.56in]{geometry}

\usepackage{calc}

\usepackage{nrcresume}

\usepackage{enumitem}
\usepackage{tabularx}

%\usepackage[scaled]{helvet}
%\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is %to be sans serif

\usepackage[T1]{fontenc}
\usepackage{setspace}

\usepackage[usenames,dvipsnames]{xcolor}

\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\WorkExperienceLineOne}[2]{%
    \nrccolstring{\textbf{#1}}{\textbf{#2}}%
}

\newcommand{\WorkExperienceLineTwo}[2]{%
    \nrccolstring{\small\textit{#1}}{\small\textit{#2}}%
}

\newcommand{\WorkExperienceMidBreak}{%
    \par \smallskip \smallskip%
}

\newcommand{\WorkExperienceEndBreak}{%
    \par\bigskip%
}

\newcommand{\makeheader}[1]{%
\begingroup%
    \noindent%
    \textcolor{MidnightBlue}{\Large \textbf{\textsc{#1\\}}}%
    \hfill%
\endgroup%
\hfill%
}
%

%%%%%%%%%%%%%%%%%%%%%%%%% Work Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\workLthree}{%
	\WorkExperienceLineOne {L-3 Ocean Systems} {Goleta, CA}
	\WorkExperienceLineTwo {Electrical Engineer II} {2011-2013}
	\WorkExperienceLineTwo {Electrical Engineer I} {2007-2011}
	\WorkExperienceLineTwo {Electrical Engineering Intern} {2007}
	\WorkExperienceMidBreak
	Lead embedded design engineer. Designed circuit cards and signal-processing systems currently in use at US Navy
	bases. Electronics design   engineer on a \$70M coastal observatory contract with the NSF and the University of
	Washington. Responsible for firmware and FPGA code on many designs. Provided engineering support for the
	manufacture and testing of hundreds of circuit boards across several product lines.
	\WorkExperienceEndBreak%
}

\newcommand{\workMotionEng}{%
	\WorkExperienceLineOne {Motion Engineering, Inc} {Goleta, CA}
	\WorkExperienceLineTwo {Engineering Intern} {2006-2007}
	\WorkExperienceMidBreak
    Engineering intern. Worked with high-performance motion controllers used in semiconductor fab plants.
    Assisted in converting several product lines to be RoHS-compliant. Worked as a component engineer to solve 
    obsolescence issues and suggest workarounds for unavailable parts. Interacted directly with global contractors.
    Auctioned and sold test equipment.
	\WorkExperienceEndBreak%
}

\newcommand{\workUCSBLifesci}{%
	\WorkExperienceLineOne {UCSB Life Sciences Department} {Goleta, CA}
	\WorkExperienceLineTwo {IT Helpdesk} {2004-2006}
	\WorkExperienceMidBreak
    Provided support for 800+ faculty, staff and graduate students in two academic departments and two
    interdisciplinary graduate programs. Responsible for basic and advanced troubleshooting to diagnose and
    resolve both hardware and software problems. Configured and maintained OS X, Linux, Windows, and FreeBSD
    computers.
	\WorkExperienceEndBreak%
}

\newcommand{\EducationUCSB}{%
    \WorkExperienceLineOne{University of California} {Santa Barbara, CA}
    \WorkExperienceLineTwo{B.S. Electrical Engineering} {2007}
	\WorkExperienceMidBreak
    Elective coursework focused on embedded systems, DSP, and technical writing. Active in student chapter of IEEE.
    Won the ITC 2006 student paper competition for a paper on vehicle-mounted 360-degree FOV camera systems.
	\WorkExperienceEndBreak%
}

\hyphenation{Micro-blaze} 

\begin{document}
%%%%%%%%%%%%%%% Title %%%%%%%%%%%%
\nrctitle
{Nicholas Clark}
{246 Mathilda Dr.}
{Goleta, CA 93117}
{805-636-4033}
{nicholas.clark@gmail.com}
%
\begin{center}\par\smallskip
\textcolor{RoyalBlue}{\Large \textbf{\textsc{Embedded Systems Designer}}}\par
\large \textbf{{Circuit Design, Firmware, Signal Processing, Technical Writing}}\par
\smallskip
\noindent \begin{minipage}[t]{0.75\textwidth}%
\begin{sloppypar}
Dymanic electrical engineer with six years experience in embedded systems. 
Good with SPICE simulation, FPGAs, microcontrollers, and DSP algorithms.
\end{sloppypar}
\end{minipage}
\end{center}
\par \bigskip
%%%%%%%%%%%%% Column 1%%%%%%%%%%%%%%%
%
%    horizontal: leftmargin, rightmargin, itemindent, listparindent, labelwidth, labelsep
%    vertical: topsep, partopsep, parsep, itemsep
%
\newcommand{\MyColumnOne}{%
    \setitemize[0]{leftmargin=*, parsep=0pt, itemsep=0pt, topsep=0pt, partopsep=0pt}%
    \noindent \begin{minipage}[t]{0.45\textwidth}%
	\par \smallskip \begin{spacing}{0.95}%

    \begin{flushleft} %
	\makeheader{Human} \par%
    \begin{itemize}%
        \item Designing for usability
        \item Technical writing
        \item Specifying and understanding design requirements
        \item Fast learner
	\end{itemize}%
	\WorkExperienceMidBreak
	\makeheader{Electrical Engineering} \par%
    \begin{itemize}%
        \item Analog and digital circuit design techniques
        \item Low-noise signal processing and filter design
        \item PCB design with OrCAD
        \item Electronics manufacturing and DFM principles
	\end{itemize}%
	\WorkExperienceMidBreak
	\makeheader{Embedded Design} \par%
    \begin{itemize}%
        \item FPGA design with Xilinx and Lattice FPGAs
        \item Microcontroller design with MSP430, AVR, and Microblaze families
        \item High-performance FPGA-based DSP
        \item Rigorous firmware design with version control and unit tests
        \item RMA and task scheduling
	\end{itemize}%
	%
	\WorkExperienceMidBreak       
	\makeheader{Software Skills} \par%
    %    
    \WorkExperienceLineOne{Engineering Software}{}
	\WorkExperienceMidBreak
    \begin{itemize}%	
		\item LTSPICE Circuit Simulator
		\item OrCAD Schematic Capture \& PCB Layout
		\item MATLAB / SIMULINK
		\item Xilinx ISE \& EDK FPGA Design Suites
		\item TI MSP430 Code Composer Studio
		\item Atmel Studio 6
	\end{itemize}%
    %
	\WorkExperienceMidBreak
    \WorkExperienceLineOne{Programming}{}
	\WorkExperienceMidBreak
    \begin{itemize}%
	    \item Verilog HDL\\
	    \item C / C++\\
	    \item Python \\
	    \item Shell scripting in BASH\\
	    \item Typesetting with \LaTeX\\
	    \item Version control with Mercurial, Subversion, and Git\\
	    \item Makefiles and GCC\\
	\end{itemize}
    %
	\WorkExperienceMidBreak
    \WorkExperienceLineOne{General Computing}{}
	\WorkExperienceMidBreak
    \begin{itemize}%
	    \item OS X, Linux, and Windows\\
	    \item Microsoft Office (Outlook, Word, Powerpoint, Excel, Visio)\\
	    \item Adobe Photoshop \& Illustrator\\
   	    \item Paint.NET \\
	\end{itemize}

\end{flushleft}%
\end{spacing} \end{minipage}%
}%
%%%%%%%%%%%%% Column 2%%%%%%%%%%%%%%%
\newcommand{\MyColumnTwo}{%
    \noindent \begin{minipage}[t]{0.45\textwidth}%
	\par \smallskip \begin{spacing}{0.95}%
	\makeheader{Work Experience} \par%
		\workLthree
		\workMotionEng
		\workUCSBLifesci
	
	\makeheader{Education} \par%
	    \EducationUCSB
	
	\makeheader{Volunteer} \par%
   	\WorkExperienceLineOne{FIRST Robotics}{Goleta, CA}
   	\WorkExperienceLineTwo{Team 1717 Engineering Mentor}{2013 Build Season}
%   	\WorkExperienceMidBreak
%
%    	\WorkExperienceLineOne{Hobbies}{}
%    	\WorkExperienceLineTwo{Programming}{}
%    	\WorkExperienceLineTwo{Web Design}{}
%    	\WorkExperienceLineTwo{Wilderness Backpacking}{}
%    	\WorkExperienceLineTwo{Playing Guitar}{}
%    	\WorkExperienceMidBreak
	\end{spacing} \end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\nrctwocols
%\begin{center}$\bullet$\end{center}\par

\noindent\begin{tabularx}{\textwidth}{@{}X|X@{}} 
\hline
{\MyColumnOne\hfill} & {\hfill\MyColumnTwo}
\end{tabularx}
\end{document}
